Conservation of interaction partners between related plants varies widely across communities and between plant families.

### 2019-07-15 manuscript/phylogenetic_signal_manuscript.tex
older changes
removed Christie from author list as per her request

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, Christie J. Webber$^{1}$, Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
University of Queensland\\Brisbane, QLD 4072, Australia }

@@

  We would like to thank the authors of the published networks used in this study. 
  We are grateful for the use of the Edward Percival field station in Kaikoura, 
  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
  the Allan Wilson Centre (to GVDR).

>>>>

\author{Alyssa R. Cirtwill$^{1,2}$, Giulio V. Dalla Riva$^{3}$, Nick J. Baker$^{1}$,\\
Mikael Ohlsson$^{4}$, Isabelle Norstr\"{o}m$^{4}$, Inger-Marie Wohlfarth Hasle$^{4}$,\\
Joshua A. Thia$^{1,5}$, 
% Christie J. Webber$^{1}$, % Christie has confirmed that she'd rather be in the acknowledgements than an author
Daniel B. Stouffer$^{1}$}
\date{\small$^1$Centre for Integrative Ecology, School of Biological Sciences\\University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^2$Present address: Department of Ecology,\\
Environment, and Plant Sciences (DEEP)\\
Stockholm University\\
114 19 Stockholm, Sweden\\
\medskip$^3$Biomathematics Research Centre, School of Mathematics and Statistics\\
University of Canterbury\\Private Bag 4800\\
Christchurch 8140, New Zealand\\
\medskip$^4$Department of Physics, Chemistry, and Biology (IFM)\\ Link\"{o}ping University\\ 581 83 Link\"{o}ping, Sweden\\
\medskip$^5$Present Address: School of Biological Sciences\\
The University of Queensland\\Brisbane, QLD 4072, Australia }

@@

  We thank Christiee J. Webber [[and others?]] for comments on the design of the 
  study and for data collection. 
  We also thank the authors of the published networks used in this study. 
  We are grateful for the use of the Edward Percival field station in Kaikoura, 
  New Zealand in May, 2014. This research was supported by an NSERC PGS-D 
  graduate scholarship (to ARC), a Marsden Fund Fast-Start grant (UOC-1101) and a 
  Rutherford Discovery Fellowship, both administered by the Royal Society of New 
  Zealand (to DBS), a BlueFern HPC PhD scholarship (to NJB), and by
  the Allan Wilson Centre (to GVDR).
